\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\title{Mustertext}
\author{Sir Thinksalot}
 
\begin{document}

\maketitle

\section{First Citation}

While traveling in France, Gilkerson and I observed many blonde women, but almost no blonde men.  Suspecting that we had stumbled upon a remarkable scientific discovery, we endured several weeks of hardship visiting the auberges and restaurants of France to gather data.  After several years of analysis and rigorous procrastination, we wrote this paper.  Much of our magnificent prose was ruthlessly eliminated by the editor to leave space for less important research.  \cite{gilkerson07}

\section{Second Citation}

'I'm learning. Why do we have one queue in front of each clerk?' Moist demanded. 'It means that if one customer takes up a lot of time, the whole queue has to wait. Then they'll start hopping sideways from one queue to another and the next thing you know someone has a nasty head wound. Have one big queue and tell people to go to the next clerk free. People don't mind a long queue if they can see that it's moving— Sorry, sir!'  \cite{moist01}

\section{Third Citation}

Its had resolving otherwise she contented therefore. Afford relied warmth out sir hearts sister use garden. Men day warmth formed admire former simple. Humanity declared vicinity continue supplied no an. He hastened am no property exercise of. Dissimilar comparison no terminated devonshire no literature on. Say most yet head room such just easy.  \cite{random99}

\subsection{Two Citations in One}

Its had resolving otherwise she contented therefore. Afford relied warmth out sir hearts sister use garden. Men day warmth formed admire former simple. Humanity declared vicinity continue supplied no an. He hastened am no property exercise of. Dissimilar comparison no terminated devonshire no literature on. Say most yet head room such just easy. \cite{gilkerson07,random99}
\newpage


\bibliographystyle{alpha}

\bibliography{references}

\end{document} 
